### 2023-08-14 manuscripts/Hussain-Hadah/Hadah-Hispanic-Last-Names.tex
edit JMP.tex

\documentclass[a4paper,fleqn]{cas-sc}

@@

\begin{abstract}
In this paper, I study discrimination against Hispanics in the labor market. I compare the children of inter-ethnic marriages to study the impact of having a Hispanic last name. While males born to Hispanic father-White mothers earn 5 percentage points less than those born to White father-Hispanic mothers, the gap could be completely explained by educational differences. I also study the effect of identifying as Hispanic on earnings. I find that men with a Spanish-sounding last name who identify as Hispanic earn significantly less than those who do not identify as Hispanic, but the gap could also be explained by educational differences.
\end{abstract}

\begin{keywords}
 Economics of Minorities, Race, and Immigrants\sep Discrimination and Prejudice\\
 \JEL{J15, J64, J71}
\end{keywords}

>>>>

\documentclass[a4paper,fleqn]{cas-sc}
\usepackage{setspace} % Load the setspace package for line spacing

% Set line spacing to double spaced
\doublespacing

@@

\begin{abstract}
\singlespacing % Set single spacing for the abstract
In this paper, I study discrimination against Hispanics in the labor market. I compare the children of inter-ethnic marriages to study the impact of having a Hispanic last name. While males born to Hispanic father-White mothers earn 5 percentage points less than those born to White father-Hispanic mothers, the gap could be completely explained by educational differences. I also study the effect of identifying as Hispanic on earnings. I find that men with a Spanish-sounding last name who identify as Hispanic earn significantly less than those who do not identify as Hispanic, but the gap could also be explained by educational differences.
\end{abstract}

\begin{keywords}
\singlespacing % Set single spacing for keywords

 Economics of Minorities, Race, and Immigrants\sep Discrimination and Prejudice\\
 \JEL{J15, J64, J71}
\end{keywords}

### 2023-08-14 my_paper/Hadah-last-names.tex
edit JMP.tex

\begin{center}
\begin{figure}[h!]
\caption{Inter-racial marriages as a percent of all marriages \\
 in the United States from 1995 to 2020.}
\includegraphics[width=\textwidth]{interracialovertime.png} 
\label{fig:3}
\end{figure}
\end{center}

@@

\begin{figure}[h!]
\centering
\caption{Chart explaining which synthetic parents and children and when we observe them.}
\begin{tikzpicture}[node distance =2cm]
\node (start) [startstop] {Synthetic Parents: Observed in 1960 to 2000. $25 \leq age \leq 40$, White, with kids};

\node (pro1) [process, below of = start, yshift = -2cm] {Children: Observed between 1994 and 2019. Born between 1954 to 1999 and $25 \leq age \leq 40$};

\draw [arrow] (start) -- (pro1);
\end{tikzpicture}
\label{flowchart1}
\end{figure}

>>>>

% \begin{center}
% \begin{figure}[h!]
% \caption{Inter-racial marriages as a percent of all marriages \\
%  in the United States from 1995 to 2020.}
% \includegraphics[width=\textwidth]{figures/Hispanics_all.png} 
% \label{fig:3}
% \end{figure}
% \end{center}

% \newpage

@@

% \newpage

% \begin{figure}[h!]
% \centering
% \caption{Chart explaining which synthetic parents and children and when we observe them.}
% \begin{tikzpicture}[node distance =2cm]
% \node (start) [startstop] {Synthetic Parents: Observed in 1960 to 2000. $25 \leq age \leq 40$, White, with kids};

% \node (pro1) [process, below of = start, yshift = -2cm] {Children: Observed between 1994 and 2019. Born between 1954 to 1999 and $25 \leq age \leq 40$};

% \draw [arrow] (start) -- (pro1);
% \end{tikzpicture}
% \label{flowchart1}
% \end{figure}
